Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-11-03 ms/ms/ms.tex

To assess the variable impacts that Caddo retouch practices may have had
on general morphology, the sample of elliptical bifaces was first binned
into two size classes using centroid size
(\href{https://seldenlab.github.io/elliptical.bifaces/}{Supplementary
Materials}). Due to potential morphological differences associated with
the use of two distinct raw materials (Kay County flint and Edwards
chert), the sample was subset by site prior to calculating the mean
centroid size for each. Raw material for bifaces from Millsap Cache were
identified by \citet{RN11461} as Kay County flint, and those from Jowell
Farm were identified as Edwards Chert due to their size, the colours
that they fluoresce beneath low and high frequency UV light, and the
paucity of similarly large locally-available raw material sources.
Bifaces larger than the mean were then assigned to the large category,
those smaller than the mean were assigned to the small category, and the
two datasets were then joined in advance of analysis
(\href{https://seldenlab.github.io/elliptical.bifaces/}{Supplementary
Materials}).

>>>>

To assess the variable impacts that Caddo retouch practices may have had
on general morphology, the sample of elliptical bifaces was binned into
two size classes using centroid size
(\href{https://seldenlab.github.io/elliptical.bifaces/}{Supplementary
Materials}). Due to potential morphological differences associated with
the use of two distinct raw materials (Kay County flint and Edwards
chert), the sample was subset by site prior to calculating the mean
centroid size for each. Raw material for bifaces from Millsap Cache were
identified by \citet{RN11461} as Kay County flint, and those from Jowell
Farm were identified as Edwards Chert due to their size, the colours
that they fluoresce beneath low and high frequency UV light, and the
paucity of similarly large locally-available raw material sources.
Bifaces larger than the mean were then assigned to the large category,
those smaller than the mean were assigned to the small category, and the
two datasets were then joined in advance of analysis
(\href{https://seldenlab.github.io/elliptical.bifaces/}{Supplementary
Materials}).
